A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-21 paper/paper.tex
theories/νType: some renames

Compared to \texttt{leY}, \texttt{leI} has no proof-irrelevance properties. This definition is specially crafted for $\filler$, where we have to reason inductively from $p \leq n$ to $n$. In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}. Then, together with computational rules stated propositionally, we reason about $\beta$-reduction of induction.

- Equality lemmas (rew_app, assoc, ...)

\section{Future work}

In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g. in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.

>>>>

Compared to \texttt{leY}, \texttt{leI} has no proof-irrelevance properties. This definition is specially crafted for $\filler$, where we have to reason inductively from $p \leq n$ to $n$. In our usage, we have lemmas \texttt{leY\_of\_leI} and \texttt{leI\_of\_leY} in order to equip \texttt{leY} with the induction scheme of \texttt{leI}. The resulting induction scheme has computational rules holding propositionally.

\section{Future work}
In the cubical case, we expect the construction to eventually provide a model of (some version of) parametric type theory~\cite{} by adding degeneracies, a hierarchy of universes (as sketched e.g. in a talk by Herbelin at the HoTT-UF workshop for the bridge case~\cite{herbelin-hott-uf}) as well as reasoning modulo permutations~\cite{grandis03}.
